### 2013-07-24 doc/asplos14/evaluation.tex
Fix up search code example and refer to it from UTS Eval section

\paragraph{Putting it all together with Unbalanced Tree Search in memory
(UTS).} 
Figure~\ref{fig:grappa-uts} shows the overall performance of \Grappa running
UTS. This experiment demonstrates that \Grappa's context
switching and communication layers can be used together, while
balancing workload, to run an irregular application efficiently.

Visiting vertices in the distributed tree requires mostly remote
accesses, and because each vertex in the tree must be visited before
it can be expanded, blocking remote reads are required. In this case,
we are forced to context switch to tolerate the remote access and
continue aggregating.

@@

We compared this to a in-memory modification of the UPC implementation
of UTS \cite{UTS}, where each core hosts a UPC ``THREAD.'' Berkeley
UPC (BUPC) is built upon GASNet, like \Grappa, but it uses RDMA transfers directly
and the compiler overlaps remote communication when possible. We expect BUPC to
perform similarly on the T3 tree, where there is little parallelism to
overlap communication and computation, and no better than T3 on T1,
given the inability to overlap vertices on each core without
multithreading (a multithreaded variant of UPC has been evaluated in
\cite{HotSLAW}). Our experiments confirm that BUPC achieves the lower throughput of
\Grappa on T3 for \emph{both} the T1 and T3 trees.

>>>>

\paragraph{Putting it all together with Unbalanced Tree Search (UTS).} 
Figure~\ref{fig:grappa-uts} shows the overall performance of \Grappa running
UTS. This experiment demonstrates that \Grappa's context
switching and communication layers can be used together, while
balancing workload, to run an irregular application efficiently.

Visiting vertices in the distributed tree requires mostly remote
accesses, and because each vertex in the tree must be visited before
it can be expanded, blocking remote reads are required. In this case,
we are forced to context switch to tolerate the remote access and
continue aggregating. Figure~\ref{fig:sample} shows a closely analogous tree search in Grappa.

@@

We compared this to a in-memory modification of the UPC implementation
of UTS \cite{UTS}, where each core hosts a UPC ``THREAD.'' Berkeley
UPC (BUPC) is built upon GASNet, like \Grappa, but it uses RDMA transfers directly
and the compiler overlaps remote communication when possible. We expect BUPC to
perform similarly on the T3 tree, where there is little parallelism to
overlap communication and computation, and no better than T3 on T1,
given the inability to overlap vertices on each core without
multithreading (a multithreaded variant of UPC has been evaluated in
\cite{HotSLAW}). Our experiments confirm that BUPC achieves lower throughput than
\Grappa for both T1 and T3 trees.

### 2013-07-24 doc/asplos14/tasks.tex
Fix up search code example and refer to it from UTS Eval section

Figure~\ref{fig:sample} shows sample code using \Grappa for a parallel tree
search. The important aspect to note is that the code looks very similar to
what would be written for single shared-memory system, without any concern about data locality or communication.

\begin{figure}[htbp]
\begin{center}
\begin{scriptsize}
\begin{lstlisting}[style=grappa]
class node_t {
  key_t   key
  int64_t numChildren;
  GlobalAddress<node_t> children;
};

void search(GlobalAddress<node_t> node, key_t key, GlobalAddress<node_t> result) {
  // deref of key is expected cache miss
  if (node->key == key) {
    delegate_write(result, node);
  } else {
    parallel_for(0, node->numChildren,
    [=](int index) {
      // first deref of children is likely miss
      search(node->children[index], key); 
    });
  }
}
\end{lstlisting}
\end{scriptsize}

    \begin{minipage}{0.95\columnwidth}
      \caption{\label{fig:sample} Sample \Grappa code illustrating a
          parallel tree search similar to the unbalanced tree search
          benchmark we describe later. The labeled cache misses occur
          if we assume the tree is not layed out in a regular fashion, which
      models more general graphs.}
    \end{minipage}

>>>>

Figure~\ref{fig:sample} shows sample code using \Grappa for a parallel tree
search. Note how the code looks very similar to a recursive search procedure for a shared-memory system, without regard for communication, and \Grappa's parallel loop construct allows easy parallelization of the search.

\begin{figure}[htbp]
\begin{center}
\begin{scriptsize}
\begin{lstlisting}[style=grappa]
class Vertex {
  Key key
  int64_t numChildren;
  GlobalAddress<Vertex> children;
};

void search(GlobalAddress<Vertex> vtx_addr,
      Key key, GlobalAddress<Vertex> result) {
  // blocking remote read to get vertex info
  Vertex vtx = delegate_read(vtx_addr);
  if (vtx.key == key) {
    // key found
    delegate_write(result, vtx);
  } else {
    // spawn stealable tasks for iterations
    parallel_for(0,vtx.numChildren,[=](int i) {
      // recursive search
      search(vtx.children+i, key, result);       
    });
  }
}
\end{lstlisting}
\end{scriptsize}

    \begin{minipage}{\columnwidth}
      \caption{\label{fig:sample} Sample \Grappa code illustrating a
        parallel tree search similar to the unbalanced tree search
        benchmark we describe later. Children are spread over the system, so each parallel recursive search performs a delegate read to get vertex data.
      }
    \end{minipage}
